---
title: "Novel oral anticoagulants network meta-analysis"
author: "Benjamin Chan"
date: "`r Sys.time()`"
output: 
  html_document: 
    keep_md: yes
    toc: yes
---


This network meta-analysis is an update to
[Fu *et al*, 2014](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC4244213/),
*J Cardiovasc Med (Hagerstown).* 2014 Dec; 15(12): 873-879.

> From: Marian McDonagh  
> Sent: Friday, January 29, 2016 4:19 PM  
> To: Benjamin Chan  
> Subject: Re: Network Meta-analysis  
> 
> OK, last email for today!
> I put it all into an excel spreadsheet --- all the outcomes.
> Looks like it might not add up to much since several outcome cells are 0's.
> Let me know what you think.

Use the [`gemtc`](https://drugis.org/software/r-packages/gemtc) package.
Check the link for references.

```{r}
library(openxlsx)
library(data.table)
library(gemtc)
```

```{r, echo=FALSE}
file.info("NOAC NMA Data.xlsx")[, c("mtime", "size")]

readSheet <- function (sheet) {
  D <- data.table(read.xlsx("NOAC NMA Data.xlsx", sheet=sheet, startRow=3, cols=1:5))
  names(D) <- c("label", "nNOAC", "yNOAC", "nWarfarin", "yWarfarin")
  D
}

tidyData <- function (D) {
  names(D) <- c("label", "nNOAC", "yNOAC", "nWarfarin", "yWarfarin")
  D <- D[, label := gsub("\\s{2,}", " ", label)]
  D <- D[, label := gsub("\\s$", "", label)]
  D <- D[, label := gsub("\\sivaroxaban", " Rivaroxaban", label)]
  D <- D[, label := gsub("0$", "0 mg", label)]
  D$study <- NA_character_
  D$noac <- NA_character_
  assignStudy <- function (str) {
    D[grep(str, label), study := str]
  }
  assignNOAC <- function (str) {
    D[grep(str, label), noac := str]
  }
  D <- assignStudy("RE-LY")
  D <- assignStudy("ENGAGE AF-TIMI")
  D <- assignStudy("Yamashita, 2012")
  D <- assignStudy("ARISTOTLE")
  D <- assignStudy("ARISTOTLE-J")
  D <- assignStudy("J-ROCKET")
  D <- assignStudy("ROCKET-AF")
  D <- assignStudy("PETRO")
  D <- assignStudy("Mao, 2014")
  D <- assignNOAC("Dabigatran 110 mg")
  D <- assignNOAC("Dabigatran 150 mg")
  D <- assignNOAC("Edoxaban 30 mg")
  D <- assignNOAC("Edoxaban 60 mg")
  D <- assignNOAC("Apixaban 5 mg")
  D <- assignNOAC("Rivaroxaban 15 mg")
  D <- assignNOAC("Rivaroxaban 20 mg")
  D <- D[, label := NULL]
  D <- melt(D, id.vars=c("study", "noac"))
  D <- rbindlist(list(merge(D[variable == "nNOAC"],
                            D[variable == "yNOAC"],
                            by=c("study", "noac")),
                      merge(D[variable == "nWarfarin"],
                            D[variable == "yWarfarin"],
                            by=c("study", "noac"))))
  D <- D[grep("NOAC", variable.x), treatment := noac]
  D <- D[grep("Warfarin", variable.x), treatment := "Warfarin"]
  D <- D[, treatment := gsub(" ", "_", treatment)]
  D <- D[, noac := NULL]
  D <- D[, `:=` (variable.x = NULL, variable.y = NULL)]
  setnames(D, c("value.x", "value.y"), c("sampleSize", "responders"))
  setkey(D, study, treatment)
  setcolorder(D, c("study", "treatment", "responders", "sampleSize"))
  D <- unique(D)
  D
}

tidyResults <- function (comparator) {
  require(data.table)
  D <- summary(relative.effect(results, comparator))$summaries$quantiles
  D <- exp(D)
  D <- data.table(treatment = rownames(D),
                  comparator = comparator,
                  D)
  D <- D[grep("^sd", treatment, invert=TRUE)]
  x <- gsub(sprintf("d\\.%s\\.", comparator), "", D[, treatment])
  D <- D[, treatment := x]
  D <- D[, c("treatment", "comparator", "50%", "2.5%", "97.5%"), with=FALSE]
  setnames(D, c("50%", "2.5%", "97.5%"), c("median", "boundLower", "boundUpper"))
  D <- D[,
         `:=` (label = gsub("_", " ", sprintf("%s vs %s", treatment, comparator)),
               result = sprintf("%.2f (%.2f, %.2f)", median, boundLower, boundUpper))]
  setcolorder(D, c("label", "result", "treatment", "comparator", "median", "boundLower", "boundUpper"))
  D
}
combineResults <- function () {
  D <- rbindlist(list(tidyResults("Apixaban_5_mg"),
                      tidyResults("Dabigatran_110_mg"),
                      tidyResults("Dabigatran_150_mg"),
                      tidyResults("Edoxaban_30_mg"),
                      tidyResults("Edoxaban_60_mg"),
                      # tidyResults("Rivaroxaban_15_mg"),
                      tidyResults("Rivaroxaban_20_mg"),
                      tidyResults("Warfarin")))
  M <- D[, .(treatment, comparator, result)]
  M <- reshape(M, idvar="treatment", timevar="comparator", direction="wide")
  M <- M[, treatment := gsub("_", " ", sprintf("%s vs", treatment))]
  setnames(M, names(M), gsub("result\\.", "", names(M)))
  setnames(M, names(M), gsub("_", " ", names(M)))
  setorder(M, treatment)
}
```

Set `linearModel`.

```{r}
effect <- "fixed"
```

Set sampler parameters.

```{r}
nAdapt <- 5000  # Burn-in
# nChain <- 4  # gemtc defaults to 4 MCMC chains; no need to set
nIter <- 20000
thin <- 10
```

Links to outcomes.

* [Mortality](mtcMortality.md)
* [Stroke](mtcStroke.md)
* [MI](mtcMI.md)
* [Bleeding](mtcBleeding.md)
