---
title: "Novel oral anticoagulants network meta-analysis"
author: "Benjamin Chan"
date: "`r Sys.time()`"
output: 
  html_document: 
    keep_md: yes
    number_sections: yes
    toc: yes
---


# Read data

> From: Marian McDonagh  
> Sent: Friday, January 29, 2016 4:19 PM  
> To: Benjamin Chan  
> Subject: Re: Network Meta-analysis  
> 
> OK, last email for today!
> I put it all into an excel spreadsheet --- all the outcomes.
> Looks like it might not add up to much since several outcome cells are 0's.
> Let me know what you think.

```{r}
library(openxlsx)
library(data.table)
list.files(getwd())
readSheet <- function (sheet) {
  D <- data.table(read.xlsx("NOAC NMA Data.xlsx", sheet=sheet, startRow=3, cols=1:5))
  names(D) <- c("label", "nNOAC", "yNOAC", "nWarfarin", "yWarfarin")
  D
}
D1 <- readSheet("Mortality")
D2 <- readSheet("Stroke")
D3 <- readSheet("MI")
D4 <- readSheet("Bleeding")
```


# Mortality

Clean up the data (do not the code).

```{r, echo=FALSE}
D <- D1
names(D) <- c("label", "nNOAC", "yNOAC", "nWarfarin", "yWarfarin")
D <- D[, label := gsub("  ", " ", label)]
D <- D[, label := gsub("\\s$", "", label)]
D <- D[, label := gsub("\\sivaroxaban", " Rivaroxaban", label)]
D <- D[, `:=` (study = NA_character_, noac = NA_character_)]
assignStudy <- function (str) {
  D[grep(str, label), study := str]
}
assignNOAC <- function (str) {
  D[grep(str, label), noac := str]
}
D <- assignStudy("RE-LY")
D <- assignStudy("ENGAGE AF-TIMI")
D <- assignStudy("Yamashita, 2012")
D <- assignStudy("ARISTOTLE")
D <- assignStudy("ARISTOTLE-J")
D <- assignStudy("J-ROCKET")
D <- assignStudy("ROCKET-AF")
D <- assignNOAC("Dabigatran 110 mg")
D <- assignNOAC("Dabigatran 150 mg")
D <- assignNOAC("Edoxaban 30 mg")
D <- assignNOAC("Edoxaban 60 mg")
D <- assignNOAC("Apixaban 5 mg")
D <- assignNOAC("Rivaroxaban 15 mg")
D <- assignNOAC("Rivaroxaban 20 mg")
D <- D[, label := NULL]
D <- melt(D, id.vars=c("study", "noac"))
D <- rbindlist(list(merge(D[variable == "nNOAC"],
                          D[variable == "yNOAC"],
                          by=c("study", "noac")),
                    merge(D[variable == "nWarfarin"],
                          D[variable == "yWarfarin"],
                          by=c("study", "noac"))))
D <- D[grep("NOAC", variable.x), treatment := noac]
D <- D[grep("Warfarin", variable.x), treatment := "Warfarin"]
D <- D[, treatment := gsub(" ", "_", treatment)]
D <- D[, noac := NULL]
D <- D[, `:=` (variable.x = NULL, variable.y = NULL)]
setnames(D, c("value.x", "value.y"), c("sampleSize", "responders"))
setkey(D, study, treatment)
setcolorder(D, c("study", "treatment", "responders", "sampleSize"))
D <- unique(D)
show(D)
```

Plot the network.

```{r mortalityNetwork}
library(gemtc)
network <- mtc.network(D)
plot(network)
```

Run the model.

```{r}
M <- mtc.model(network, type="consistency")
system.time(results <- mtc.run(M, thin=10))
```

Sampler diagnostics.

```{r mortalityGelman, fig.height=8}
gelman.plot(results)
```

Sampler diagnostics.

```{r mortalityTrace, fig.height=10}
plot(results)
```

Summary.

```{r mortalityForest}
summary(results)
forest(results)
```
