---
title: "NOAC network meta-analysis: Bleeding"
author: "Benjamin Chan"
date: "`r Sys.time()`"
output: 
  html_document: 
    keep_md: yes
    toc: yes
---

[Back](README.md) to main page.

Read data.

```{r}
D <- readSheet("Bleeding")
D <- D[!is.na(label)]
D <- D[,
       `:=` (nWarfarin = as.numeric(nWarfarin),
             yWarfarin = as.numeric(yWarfarin))]
```

Hard-code data corrections and additions to the PETRO study.

> From: Marian McDonagh  
> Sent: Friday, March 11, 2016 4:17 PM  
> To: Benjamin Chan  
> Subject: Re: Network Meta-analysis  
> 
> Hi Ben,  
> Yes, I was noticing the Dabi 300mg problem.
> We should definitely exclude that dose as it is not used (too much bleeding).
> There were three dabi 150 arms (with varying aspirin doses).
> Since the aspirin made no difference, and other studies allow its use, we can use all 3 arms.
> But, the major bleeding events were still 0 across those.
> The total N for that is actually 169.
> And of course the 70 patients on warfarin with no events also.

```{r}
D <- D[label != "PETRO Dabigatran 300 mg"]
D <- D[label == "PETRO Dabigatran 150 mg", nNOAC := 169]
```

Tidy up the data and bias the warfarin arm of ROCKET-AF to be similar to the Rivaroxaban arm.

```{r, results='asis'}
D <- tidyData(D)
D <- biasROCKETAF()
write.csv(D, file="mtcBleedingData.csv", row.names=FALSE)
print(xtable(D, digits=rep(0, 5)), type="html", include.rownames=FALSE)
D <- D[!is.na(responders)]
network <- mtc.network(D)
```

Run the model using `r sprintf("%s-effects", effect)`.

```{r, child="model.Rmd"}
```

# Summary

Direct and indirect odds ratios and 95% confidence bounds are stored in
[mtcBleedingOddsRatios.csv](mtcBleedingOddsRatios.csv).

```{r, results='asis'}
or <- combineResults(outcomeBleeding=TRUE)
write.csv(or, file="mtcBleedingOddsRatios.csv", row.names=FALSE)
print(xtable(or), type="html", include.rownames=FALSE)
```

# Forest plots, NOAC vs NOAC

```{r, child="forestPlots.Rmd"}
```

# Diagnostics

```{r, child="modelDiagnostics.Rmd"}
```
