---
title: "NOAC network meta-analysis: Stroke"
author: "Benjamin Chan"
date: "`r Sys.time()`"
output: 
  html_document: 
    keep_md: yes
    toc: yes
---

[Back](README.md) to main page.

Read data.

```{r}
D <- readSheet("Strokeembolism")
```

Hard-code data corrections and additions to the PETRO study.

> From: Marian McDonagh  
> Sent: Friday, March 11, 2016 4:17 PM  
> To: Benjamin Chan  
> Subject: Re: Network Meta-analysis  
> 
> For stroke, you are right --- we can delete row 18, and correct the N for dabi 150 to be 169 in row 6.  
> 
> From: Benjamin Chan  
> Sent: Friday, March 11, 2016 4:08 PM  
> To: Marian McDonagh  
> Subject: RE: Network Meta-analysis  
> 
> Marian,
>  
> Also, for the stroke outcome, you have PETRO dabigatran 150 mg listed twice (rows 6 and 18).
> I'm guessing row 6 is for dabi 300 mg.
> Same question, though.
> Should I exclude the 300 mg arm?

```{r}
D <- D[1:(nrow(D) - 1)]
D <- D[label == "PETRO Dabigatran 150 mg", nNOAC := 169]
```

Tidy up the data.

```{r, results='asis'}
D <- tidyData(D)
write.csv(D, file="mtcStrokeData.csv", row.names=FALSE)
print(xtable(D, digits=rep(0, 5)), type="html", include.rownames=FALSE)
network <- mtc.network(D)
```

Run the model using `r sprintf("%s-effects", effect)`.

```{r, child="model.Rmd"}
```

# Summary

Direct and indirect odds ratios and 95% confidence bounds are stored in
[mtcStrokeOddsRatios.csv](mtcStrokeOddsRatios.csv).

```{r, results='asis'}
or <- combineResults()
write.csv(or, file="mtcStrokeOddsRatios.csv", row.names=FALSE)
print(xtable(or), type="html", include.rownames=FALSE)
```

# Forest plots, NOAC vs NOAC

```{r, child="forestPlots.Rmd"}
```

# Diagnostics

```{r, child="modelDiagnostics.Rmd"}
```
